Mathematical appendix to "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2022-06-19 src/docs_paper/appendix.Rmd
Include coverage assessment plot in appendix #128

<!-- \begin{figure} -->
<!--   \centering -->
<!--   \makebox[\textwidth][c]{\includegraphics{figures/coverage.jpeg}} -->
<!--   \caption{Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the selected models. These plots are adapted from \citet{sailynoja2021graphical} and are an example of posterior predictive checks, see e.g. \citet[Chapter 6.1]{gelman2020bayesian}.} -->
<!--   \label{fig:coverage} -->
<!-- \end{figure} -->

@@

@@

>>>>

@@

To fill: explanation of Table \ref{tab:logistic-model-performance} and Figure \ref{fig:logistic-model-performance}.

@@

## Coverage assessment

To fill: explanation of Figure \ref{fig:coverage}.

\begin{figure}
  \centering
  \makebox[\textwidth][c]{\includegraphics{depends/coverage.jpeg}}
  \caption{Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the final selected models. These plots are adapted from \citet{sailynoja2021graphical} and are an example of posterior predictive checks, see for example \citet[Chapter 6.1]{gelman2020bayesian}.}
  \label{fig:coverage}
\end{figure}
